### 2017-02-20 frontmatter.tex
Hhh edit

% Declaration
\begin{declaration}
  \vspace*{1cm}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
The work for the analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results presented in chapter \ref{chap:hhh} I 
was responsible for the statistical inference. This included
the interpretation of the results in MSSM and two Higgs doublet model benchmark scenarios. The 
work is included in Ref. \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for three out of four channels presented in the final version of the analysis,
evaluation of systematic uncertainties in all four channels, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work presented in chapter \ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.

>>>>

% Declaration
\begin{declaration}
  \vspace*{1cm}
  I declare that the work in this thesis is mine. Figures and results taken from other sources
include the appropriate reference in the text or figure caption. Figures labelled `CMS' are sourced
directly from CMS publications. The `CMS Preliminary' label indicates figures which
have been made public via a preliminary public document or a public website, but are not
included in a publication in a peer-reviewed journal. Figures labelled `CMS' or `CMS preliminary', 
including those made by myself, include the relevant reference in the figure caption.
The work for the analyses presented in chapters \ref{chap:hhh} and \ref{chap:mssm} was 
carried out as part of the CMS \Htotautau working group, and in collaboration with other members of the group.
For the results presented in chapter \ref{chap:hhh} I contributed to the data analysis of two out of three
final states presented in the final public result, and I 
was responsible for the statistical inference. This included
the interpretation of the results in MSSM and two Higgs doublet model benchmark scenarios. The 
work is included in Ref. \cite{CMS-HIG-14-034}. For the results presented in chapter \ref{chap:mssm}
I was responsible for all stages of the analysis, including the optimisation
of object selection and event categorisation, as well as studies of background
methods for three out of four channels presented in the final version of the analysis,
evaluation of systematic uncertainties in all four channels, and production of the statistical
results, including model interpretations. This work is included in the most recent
preliminary result \cite{CMS-PAS-HIG-16-037}, as well as a predating preliminary
result using a smaller dataset \cite{CMS-PAS-HIG-16-006}.
The work presented in chapter \ref{sec:mssm_combination} has
not been made public, and draws on the results of \cite{CMS-PAS-HIG-16-037} and \cite{CMS-PAS-HIG-16-006}.
